Parallel Monte Carlo Synthetic Acceleration Methods for Discrete Transport Problems

### 2013-09-04 doc/dissertation/presentation/defense.tex
updating weak scaling slide
updating slides build

%%---------------------------------------------------------------------------%%
\begin{frame}{Research Outline}
  \begin{itemize}
  \item Development of a linear scheme for the $SP_N$ equations
    leveraging Monte Carlo Synthetic Acceleration
    \medskip
    \begin{itemize}
    \item Application to neutron transport
    \item Research is required to study MCSA preconditioning
    \item Iterative performance is of concern
    \end{itemize}
    \bigskip
  \item Development of a nonlinear scheme for the Navier-Stokes
    equations leveraging Monte Carlo Synthetic Acceleration
    \medskip
    \begin{itemize}
    \item Monte Carlo is a more natural fit
    \item Application to fluid flow
    \item Convergence of the linear model is of concern
    \end{itemize}
    \bigskip
  \item Parallelization of Monte Carlo Synthetic Acceleration
    \medskip
    \begin{itemize}
    \item Parallel strategies taken from modern reactor physics
      methods
    \item Research is required to explore varying parallel strategies
    \item Parallel scalability is of concern
    \end{itemize}
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    {\small
    \item Drekar is a production CFD code using Newton methods with
      FAD
      \medskip
    \item MCLS incorporated into Drekar nonlinear scheme to implement
      FANM
      \medskip
    \item Newton-Krylov method with Aztec GMRES used for benchmark
      comparisons
    \item All methods and problems preconditioned with explicit scheme
      using algebraic multigrid (ML) and leveraged some kind of
      globalization (e.g. backtracking) with RDA
    }
  \end{itemize}

@@

      \begin{figure}[htpb!]
        \begin{center}
          \includegraphics[width=2.3in]{titan_pure_weak_time.pdf}
        \end{center}
%        \caption{Wall Time.}
      \end{figure}

      \begin{figure}[htpb!]
        \begin{center}
          \includegraphics[width=2.3in]{titan_weak_implementation.pdf}
        \end{center}
%        \caption{Implementation Efficiency.}
      \end{figure}

@@

      \begin{figure}[htpb!]
        \begin{center}
          \includegraphics[width=2.3in]{titan_weak_absolute.pdf}
        \end{center}
%        \caption{Absolute Efficiency.}
      \end{figure}

      {\small
        \begin{itemize}
        \item Krylov implementation efficiencies drop with
          reduced iteration count
        \item MCSA maintained constant number of iterations
        \end{itemize}
      }

@@

>>>>

%%---------------------------------------------------------------------------%%
\begin{frame}{Research Outline}
  \begin{itemize}
  \item Development of a linear scheme for the $SP_N$ equations
    leveraging Monte Carlo Synthetic Acceleration
    \begin{itemize}
    \item Application to neutron transport
    \item Research is required to study MCSA preconditioning
    \item Iterative performance is of concern
    \end{itemize}
    \bigskip
  \item Development of a nonlinear scheme for the Navier-Stokes
    equations leveraging Monte Carlo Synthetic Acceleration
    \begin{itemize}
    \item Monte Carlo is a more natural fit
    \item Application to fluid flow
    \item Convergence of the linear model is of concern
    \end{itemize}
    \bigskip
  \item Parallelization of Monte Carlo Synthetic Acceleration
    \begin{itemize}
    \item Parallel strategies taken from modern reactor physics
      methods
    \item Research is required to explore varying parallel strategies
    \item Parallel scalability is of concern
    \end{itemize}
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    {\small
    \item Drekar is a production CFD code using Newton methods with
      FAD
      \medskip
    \item MCLS incorporated into Drekar nonlinear scheme to implement
      FANM
      \medskip
    \item Newton-Krylov method with Aztec GMRES used for benchmark
      comparisons
    \item All methods and problems preconditioned with explicit scheme
      using algebraic multigrid (ML) with RDA and leveraged some kind
      of globalization (e.g. backtracking) }
  \end{itemize}

@@

      \begin{figure}[htpb!]
        \begin{center}
          \includegraphics[width=2.3in]{titan_pure_weak_time.pdf}
        \end{center}
        \caption{Wall Time.}
      \end{figure}

      %% \begin{figure}[htpb!]
      %%   \begin{center}
      %%     \includegraphics[width=2.3in]{titan_weak_implementation.pdf}
      %%   \end{center}
      %%   \caption{Implementation Efficiency.}
      %% \end{figure}

@@

      \begin{figure}[htpb!]
        \begin{center}
          \includegraphics[width=2.3in]{titan_weak_absolute.pdf}
        \end{center}
        \caption{Absolute Efficiency.}
      \end{figure}

@@

  {\small
    \begin{itemize}
    \item Spectral radius maintained by growing the global boundary
    \item MCSA maintained constant number of iterations
    \item Krylov iteration count reduced as a function of problem size
    \end{itemize}
  }
